A Geometry for Network Visualization in \MakeLowercase{\texttt{ggplot2}}

### 2015-03-30 CC/writeup.Rnw
email example

\maketitle
\begin{abstract}
Abstract will be here
\end{abstract}
<<chunk_setup, echo=FALSE>>=
library(knitr)
opts_chunk$set(tidy = FALSE, echo=FALSE, cache=FALSE, eval = TRUE, message = FALSE, warning = FALSE,  fig.height = 8, fig.width = 8, fig.align = 'center',fig.show='hide')
@
<<readingdata, eval=TRUE, echo=FALSE>>=
library(ggplot2) # needs to be the version with geom_net!
 theme_net <- theme(aspect.ratio = 1, line = element_blank(), panel.background = element_blank(), plot.background = element_blank(), axis.text=element_blank(),axis.title=element_blank())
 data(blood, football, theme_elements, lesmis)
names(blood$vertices)[1] <- 'label'
load("data/madmen.rda") # relative path should work for both of us
names(madmen$vertices)[1] <- 'label'
names(theme_elements$vertices)[1] <- 'label'
football$vertices$label <- as.factor(football$vertices$label)
football$vertices$value <- as.factor(football$vertices$value)
football$edges$in.conf <- 0
for (i in 1:nrow(football$edges)){
  idx1 <- which(football$vertices$label == football$edges$from[i])
  idx2 <- which(football$vertices$label == football$edges$to[i])
  if (football$vertices$value[idx1] == football$vertices$value[idx2]){
    football$edges$in.conf[i] <- 1
  }
}
email.net <- read.csv("data/email-data.csv")
email.names <- data.frame(label = as.factor(unique(c(as.character(email.net$From),as.character(email.net$to)))))
library(plyr)
email.net <- ddply(email.net, .(eID), transform, nrecipients=length(to))
employee <- read.csv("data/EmployeeRecords.csv")
employee <- merge(email.names, employee, by.x="label", by.y="EmailAddress", all.x=T)
library(RColorBrewer)
cols <- brewer.pal(8, name="Set1")
@

>>>>

\maketitle
\begin{abstract}
Abstract will be here
\end{abstract}
<<chunk_setup, echo=FALSE>>=
library(knitr)
opts_chunk$set(tidy = FALSE, echo=FALSE, cache=FALSE, eval = TRUE, message = FALSE, warning = FALSE,  fig.height = 8, fig.width = 8, fig.align = 'center',fig.show='hide')
@
<<readingdata, eval=TRUE, echo=FALSE>>=
library(ggplot2) # needs to be the version with geom_net!
 theme_net <- theme(aspect.ratio = 1, line = element_blank(), panel.background = element_blank(), plot.background = element_blank(), axis.text=element_blank(),axis.title=element_blank())
 data(blood, football, theme_elements, lesmis)
names(blood$vertices)[1] <- 'label'
load("data/madmen.rda") # relative path should work for both of us
names(madmen$vertices)[1] <- 'label'
names(theme_elements$vertices)[1] <- 'label'
football$vertices$label <- as.factor(football$vertices$label)
football$vertices$value <- as.factor(football$vertices$value)
football$edges$in.conf <- 0
for (i in 1:nrow(football$edges)){
  idx1 <- which(football$vertices$label == football$edges$from[i])
  idx2 <- which(football$vertices$label == football$edges$to[i])
  if (football$vertices$value[idx1] == football$vertices$value[idx2]){
    football$edges$in.conf[i] <- 1
  }
}
load("data/email.rda")
#email.net <- read.csv("data/email-data.csv")
#email.names <- data.frame(label = as.factor(unique(c(as.character(email.net$From),as.character(email.net$to)))))
#library(plyr)
#email.net <- ddply(email.net, .(eID), transform, nrecipients=length(to))
#employee <- read.csv("data/EmployeeRecords.csv")
#employee <- merge(email.names, employee, by.x="label", by.y="EmailAddress", all.x=T)
email.net <- email$edges
employee <- email$nodes
library(RColorBrewer)
cols <- brewer.pal(8, name="Set1")
@
